---
title: "Laura Acion's Resume"
author: Laura Acion
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

# Load csv with position info
position_data <- read_csv('positions.csv')

# to print:: pagedown::chrome_print()

```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("View this CV online with links here https://lauracion.github.io/my_cv/")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this doc](https://github.com/lauracion/my_cv/blob/master/Acion_Resume.pdf)")
}
```

Contact {#contact}
-------------------------------------------------------------------------------
- <i class="fa fa-envelope"></i> lacion@gmail.com
- <i class="fa fa-home"></i> [lacion.rbind.io](https://lacion.rbind.io)
- <i class="fa fa-twitter"></i> [\@\_lacion\_](https://twitter.com/_lacion_)
- <i class="fa fa-github"></i> [github.com/lauracion](https://github.com/lauracion)


Skills {#skills}
-------------------------------------------------------------------------------


### Statistical Programming:

- R

- SAS

- SPSS

### Other Tools:

- Shell scripting

- Git, Github

- Visual Basic

### Languages {#languages}

- **Spanish:** Native language

- **English:** Fully fluent (TOEFL)

- **French:** Fully fluent (DALF)



Main
===============================================================================
Laura Acion Resume {#title}
-------------------------------------------------------------------------------


```{r}
intro_text <- "I am a tenured Associate Researcher at the Argentinean National Research Council (CONICET) working at the Calculus Institute, University of Buenos Aires (UBA). I lead a health data science research group in formation. One of the main goals of the group is to transition from paid-wall to open science. 

Another of my main career goals it to improve data analysis teaching and practice. One of the roles I enjoy most is mentoring others. I am active in international collaborative teaching and programming communities with high diversity standards. These communities help me achieve my goals, particularly in Latin America, while giving back to open source."

cat(sanitize_links(intro_text))
```


Selected Education {data-icon=graduation-cap data-concise=true}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```


Selected Research Experience {data-icon=laptop}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'research_positions')
```


Selected Teaching Experience {data-icon=chalkboard-teacher}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'teaching_positions')
```


Selected Proffesional Activities {data-icon=briefcase}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'prof_activities')

```

Selected Editorial Experience {data-icon=book-open}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'ed_exp')

```


Selected Community Developments {data-icon=group}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'community_projects')
```

Selected Talks and Presentations {data-icon=group}
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'talks')

```

Peer-Reviewed Publications {data-icon=book-open}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'pubs')

```


Selected Awards and Scholarships
-------------------------------------------------------------------------------

```{r}
print_section(position_data, 'awards')

```

::: aside

Find my full CV [**here**](http://tiny.cc/Acion_CV)



-------------------------------------------------------------------------------
Made with the R package [**pagedown**](https://github.com/rstudio/pagedown) 

Code available [**here**](https://github.com/lauracion/my_cv)

Last updated on `r Sys.Date()`

:::


```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


